PWNCAT2

### 2012-07-19 pwncatalog/PWNCAT2/paper/subsections/offpeak_analysis_method.tex
update

We develope a procedure for characterizing any emission found
in off-peak phase internals for the pulsars in this catalog.  
This proceure used both the spectral and spatial characteristics
of any observed emission to determine the physical origin of the emission.

Pulsar wind nebula are expected in many cases to be spatially
extended. For example, \velax and HESS\;J1825-137 are PWN
that have been observed by the \lat to be spatially extended
\citep{LAT_collaboration_Vela_X_2010,LAT_collaboration_HESS_J1825_2011}.
On the other hand, not all pulsar wind nebula are expected to be
significantly spatially resolved at \gev energies due to the finite
instrument resolution of the LAT. For example, the Crab nebula appears
as a point-like source in the LAT but is distinuished in the off-peak
from the Crab pulsar by its hard spectrum for E$\gtrsim$1 \gev.
\citep{LAT_collaboration_crab_2010}.

On the other hand, a previous analysis by the Fermi LAT collaboration
found seven off-peak regions to have significant emission which is
point-like in nature that is characterized by a pulsar-like cutoff
spectrum \citep{LAT_collaboration_PWNCAT_2011}.  We can thefore use
either spatial extension or significant emission at high energy to
distinguish the PWN scenario and point-like emission with a cutoff
spectrum to distingiugh the pulsar scenario.

To perform this test, we used the likelihood fitting pacakge \pointlike
to study the spatial character of emission in the off-peak regions
and \gtlike in binned model to study the spectral character of
the emission. These tools provide complementary features and this
method is very similar to the approach used in the second \lat catalog
\citep{LAT_Collaboration_2FGL_2012} and a followup search for spatially
extended sources \citep{LAT_collaboration_extended_search_2012}.

@@

After fitting the position of a source, we use \gtlike to perform a likelihood-ratio test for
the detection of the source. Here, \ts is defined as
\begin{equation}
  \ts = 2 \log(\likelihood_\text{pt}/\likelihood_\text{bg})
\end{equation}
where $\likelihood_\text{pt}$ is the Poission likelihood for a model including the source and $\likelihood_\text{bg}$
the likelihood for a model not including the source.
We set the threshold for detection of signfiicant emission at $\ts>25$, 
corresponding to a significance just over $4\sigma$ \citep{LAT_Collaboration_1FGL_2010}.

>>>>

We developed a procedure for characterizing emission found
in off-peak phase region for all pulsars in this catalog.  
This procedure used both the spectral and spatial characteristics
of any observed emission to determine the physical origin of the emission.

PWNe are often expected to be spatially
resolvable at GeV energies. For example, \velax and HESS\;J1825-137 are PWN
that have been spatially resolved by the \lat 
\citep{LAT_collaboration_Vela_X_2010,LAT_collaboration_HESS_J1825_2011}.
On the other hand, not all PWN are expected to be
significantly spatially resolved due to the finite
instrument resolution of the LAT. For example, the Crab nebula appears
as a point-like source in the LAT but is distinguished from the Crab
pulsar in the off-peak region by its hard spectrum for E$\gtrsim$1 \gev.
\citep{LAT_collaboration_crab_2010}.

On the other hand, pulsars can have DC emission in the off-peak region
due to the geometry of the pulsar's magnetosphere.  A previous analysis
by the LAT collaboration found five off-peak regions to have significant
emission which is point-like in nature that is characterized by a
pulsar-like cutoff spectrum \citep{LAT_collaboration_PWNCAT_2011}.
We can therefore use either spatial extension or a hard spectrum to
distinguish a PWN scenario and point-like emission with a cutoff spectrum
to distinguish the pulsar scenario.

To perform this test, we used the likelihood fitting package \pointlike
to study the spatial character of emission in the off-peak regions
and \gtlike in binned model to study the spectral character of
the emission. These tools provide complementary features and this
method is very similar to the approach used in the second \lat catalog
\citep{LAT_Collaboration_2FGL_2012} and a follow up search for spatially
extended sources \citep{LAT_collaboration_extended_search_2012}.

@@

After fitting the position of a source, we use \gtlike to perform a
likelihood-ratio test for the detection of the source. Here, \ts is
defined as
\begin{equation}
  \ts = 2 \log(\likelihood_\text{pt}/\likelihood_\text{bg})
\end{equation}
where $\likelihood_\text{pt}$ is the Poisson likelihood for a model
including the source and $\likelihood_\text{bg}$ the likelihood for a
model not including the source.  We set the threshold for detection of
significant emission at $\ts>25$, corresponding to a significance just
over $4\sigma$ \citep{LAT_Collaboration_1FGL_2010}.
